---
title: "Batting"
---

<hr>

```{r Setup,label = "SETUP", include=FALSE, results = 'hide'}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", comment = NA, warning = FALSE, message = FALSE)
library(utils)
library(dplyr)
library(stringr)
library(ggplot2)
library(gridExtra)
library(plotly)
master <- read.csv("master.csv")
hitter <- master %>%
  filter(BatterTeam == "APP_MOU" | BatterTeam == "APP_PRA" | Date <= "10/01/2019")
```

```{r Batter Summary}
s <- sum(str_count(hitter$PlayResult, "Single"))
do <- sum(str_count(hitter$PlayResult, "Double"))
t <- sum(str_count(hitter$PlayResult, "Triple"))
hr <- sum(str_count(hitter$PlayResult, "HomeRun"))
hit <- sum(s + do + t + hr)
inpl <- sum(str_count(hitter$PitchCall, "InPlay"))
rbi <- sum(hitter$RunsScored)
bb <- sum(str_count(hitter$KorBB, "Walk"))
hbp <- sum(str_count(hitter$PitchCall, "HitByPitch"))
walk <- sum(hbp + bb)
sac <- sum(str_count(hitter, "Sacrifice"))
es <- hitter %>%
  filter(PitchCall == "InPlay" & ExitSpeed & !hitter$HitType == "Bunt")
la <- hitter %>%
  filter(PitchCall == "InPlay" & Angle & !hitter$HitType == "Bunt")
so <- sum(str_count(hitter$KorBB, "Strikeout"))
pa <- inpl + walk + so
ab <- pa - walk - sac
avg <- hit / ab
obp <- (hit + walk) / pa
tb <- sum(s + (2 * do) + (3 * t) + (4 * hr)) 
slg <- tb / ab
ops <- obp + slg
```

| | | | | | | Hitting Summary
-|-|-|-|-|-|-|-
PA:|`r pa`| 2B:| `r do` | RBI: |`r rbi`| AVG: |`r sprintf("%.3f", avg)` |
AB: |`r ab` | 3B: | `r t` | BB: |`r bb` |SLG: | `r sprintf("%.3f", slg)`|
Hits: |`r hit`| HR: | `r hr` | HBP: | `r hbp` | OPS: | `r sprintf("%.3f", ops)`|
 | SO: |`r so` ||||| OBP: | `r sprintf("%.3f", obp)`

Hits| | 
-|-|
AVG Exit Velocity: | `r sprintf("%.2f", mean(es$ExitSpeed, na.rm = TRUE))` mph
Max Exit Velocity: | `r sprintf("%.2f", max(es$ExitSpeed, na.rm = TRUE))` mph
AVG Launch Angle: | `r sprintf("%.2f", mean(la$Angle, na.rm = TRUE))` degrees
Max Estimated Distance: | `r sprintf("%.2f", max(hitter$Distance, na.rm = TRUE))` feet

```{r Strike Zone/Home Plate/Batter Mapping}
x <- c(-.95,.95,.95,-.95,-.95)
y <- c(1.6,1.6,3.5,3.5,1.6)
sz <- data_frame(x, y)

x1 <- c(-.95, -.95, 0, .95, .95, -.95)
y1 <- c(0, .15, .25, .15, 0, 0)
hp <- data_frame(x1, y1)

x2 <- c(1.61, 3.11, 3.11, 1.61, 1.61)
y2 <- c(0, 0, 5.5, 5.5, 0)
rhb <- data_frame(x2, y2)

x4 <- c(-1.61, -3.11, -3.11, -1.61, -1.61)
y4 <- c(0, 0, 5.5, 5.5, 0)
lhb <- data_frame(x2, y2)

x3 <- c(2.36)
y3 <- c(2.75)

x5 <- c(-2.36)
y5 <- c(2.75)
```

<center>
```{r Spray Chart}
hitter$Bearing <- ((hitter$Bearing * -1) + 90)*pi/180
hitter$x <- hitter$Distance*cos(hitter$Bearing)
hitter$y <- hitter$Distance*sin(hitter$Bearing)
bases <- data.frame(xa = c(0, 90/sqrt(2), 0, -90/sqrt(2), 0, rep(0)),
ya = c(0, 90/sqrt(2), 2 * 90/sqrt(2), 90/sqrt(2), 0, rep(0)))
sprayfilter <- hitter %>%
  filter(!PlayResult == "Undefined" & !PlayResult == "Sacrifice")
bb <- ggplot(bases, aes(x = xa, y = ya)) + 
  geom_path() + 
  geom_point(data = sprayfilter, x = sprayfilter$x, y = sprayfilter$y, 
             aes(color = factor(sprayfilter$PlayResult), 
                 text = paste("Exit Speed: ", ExitSpeed, 
                               "<br> Distance: ", Distance,
                               "<br> Launch Angle: ", Angle))) + 
  geom_segment(x = 0, xend = -233.35, y = 0, yend = 233.35) +
  geom_segment(x = -233.35, xend = -160.59, y = 233.35, yend = 340) + 
  geom_segment(x = -160.59, xend = -49.36, y = 340, yend = 401.98) +
  geom_segment(x = -49.36, xend = 49.36, y = 401.98, yend = 401.98) +
  geom_segment(x = 49.36, xend = 157.67, y = 401.98, yend = 338.05) +
  geom_segment(x = 157.67, xend = 229.81, y = 338.05, yend = 229.81) +
  geom_segment(x = 229.81, xend = 0, y = 229.81, yend = 0) +
  xlim(-250, 250) + ylim(-10, 500) +
  theme(axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.background = element_blank(),
      legend.title = element_blank()) +
  coord_equal() +
  scale_color_discrete(limits = c("Single" ,"Double", "Triple", "HomeRun", "Out", "FieldersChoice", "Error"))
ggplotly(bb, tooltip = "text")
```

```{r Ninety Plus}
NinetyPlus <- hitter %>%
  filter(ExitSpeed >= 90)
np <- ggplot() +
  geom_path(data = sz, aes(x = x, y = y)) +
  geom_path(data = rhb, aes(x = x2, y = y2), color = "lightgray") +
  geom_path(data = lhb, aes(x = x4, y = y4), color = "lightgray") +
  geom_text(mapping = aes(x = x3, y = y3), label = paste("RHB"), color = "lightgray") +
  geom_text(mapping = aes(x = x5, y = y5), label = paste("LHB"), color = "lightgray") +
  geom_polygon(hp, mapping = aes(x = x1, y = y1), color = "black", fill = "white") +
  coord_equal() +
  ggtitle("90+ Exit Velocities") +
  geom_point(data = NinetyPlus,
             aes(x = PlateLocSide, y = PlateLocHeight, color = TaggedPitchType, 
                 text = paste("Pitch Type: ", TaggedPitchType, "<br>Exit Speed: ", ExitSpeed, "<br> Distance: ", Distance, "<br> Launch Angle: ", Angle))) +
  scale_color_discrete(limits = c("Fastball" ,"ChangeUp", "Splitter", "Curveball", "Slider")) +
  coord_cartesian(xlim = c(-4.5, 4.5), ylim = c(0, 5.5)) +
  theme(axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.background = element_blank(),
      legend.title = element_blank())
ggplotly(np, tooltip = "text")
```

```{r Fastball Takes}
FastballTakes <- hitter %>%
  filter(TaggedPitchType == "Fastball" & PitchCall == "StrikeCalled")
FastballTakes$Count <- paste(FastballTakes$Balls, "-", FastballTakes$Strikes, "") 
ft <- ggplot() +
  geom_path(data = sz, aes(x = x, y = y)) +
  geom_path(data = rhb, aes(x = x2, y = y2), color = "lightgray") +
  geom_path(data = lhb, aes(x = x4, y = y4), color = "lightgray") +
  geom_text(mapping = aes(x = x3, y = y3), label = paste("RHB"), color = "lightgray") +
  geom_text(mapping = aes(x = x5, y = y5), label = paste("LHB"), color = "lightgray") +
  geom_polygon(hp, mapping = aes(x = x1, y = y1), color = "black", fill = "white") +
  coord_equal() +
  xlab("Plate Width") +
  ylab("Plate Height") +
  ggtitle("Fastball Takes") +
  geom_point(data = FastballTakes,aes(x = PlateLocSide, y = PlateLocHeight, color = TaggedPitchType, text = paste("Count: ", Count))) +
  coord_cartesian(xlim = c(-4.5, 4.5), ylim = c(0, 5.5)) +
  theme(axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.background = element_blank(),
      legend.title = element_blank())
ggplotly(ft, tooltip = "text")
```

```{r Whiffs}
Whiffs <- hitter %>%
  filter(PitchCall == "StrikeSwinging")
wh <- ggplot() +
  geom_path(data = sz, aes(x = x, y = y)) +
  geom_path(data = rhb, aes(x = x2, y = y2), color = "lightgray") +
  geom_path(data = lhb, aes(x = x4, y = y4), color = "lightgray") +
  geom_text(mapping = aes(x = x3, y = y3), label = paste("RHB"), color = "lightgray") +
  geom_text(mapping = aes(x = x5, y = y5), label = paste("LHB"), color = "lightgray") +
  geom_polygon(hp, mapping = aes(x = x1, y = y1), color = "black", fill = "white") +
  coord_equal() +
  xlab("Plate Width") +
  ylab("Plate Height") +
  ggtitle("Swings & Misses") +
  geom_point(data = Whiffs,aes(x = PlateLocSide, y = PlateLocHeight, color = TaggedPitchType, text = paste("Pitch Type: ", TaggedPitchType, "<br>Velocity: ", RelSpeed, "<br>Spin Rate: ", SpinRate))) +
  scale_color_discrete(limits = c("Fastball" ,"ChangeUp", "Splitter", "Curveball", "Slider")) +
  coord_cartesian(xlim = c(-4.5, 4.5), ylim = c(0, 5.5)) +
  theme(axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      plot.background = element_blank(),
      legend.title = element_blank())
ggplotly(wh, tooltip = "text")
```
</center>

<hr>