---
title: "Team Batting"
---

<hr>

```{r Setup,label = "SETUP", include=FALSE, results = 'hide'}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", comment = NA, warning = FALSE, message = FALSE)
library(utils)
library(dplyr)
library(stringr)
library(ggplot2)
library(gridExtra)
library(plotly)
library(lubridate)
library(scales)
master <- read.csv("2020-2021.csv")
master$Date <- as.Date(master$Date , "%m/%d/%Y")
hitter <- master %>%
  filter(BatterTeam == "APP_MOU" | BatterTeam == "APP_PRA")
```

```{r Batter Summary}
s <- sum(str_count(hitter$PlayResult, "Single"))
do <- sum(str_count(hitter$PlayResult, "Double"))
t <- sum(str_count(hitter$PlayResult, "Triple"))
hr <- sum(str_count(hitter$PlayResult, "HomeRun"))
hit <- sum(s + do + t + hr)
inpl <- sum(str_count(hitter$PitchCall, "InPlay"))
hh <- hitter %>%
  filter(ExitSpeed >= 90)
hh <- nrow(hh)
hhavg <- hh / inpl
qh <- hitter %>%
  filter(ExitSpeed >= 90) %>%
  filter(Angle >= 10 & Angle < 32)
qh <- nrow(qh)
qhavg <- qh / inpl
rbi <- sum(hitter$RunsScored)
bb <- sum(str_count(hitter$KorBB, "Walk"))
hbp <- sum(str_count(hitter$PitchCall, "HitByPitch"))
walk <- sum(hbp + bb)
sac <- sum(str_count(hitter, "Sacrifice"))
es <- hitter %>%
  filter(PitchCall == "InPlay" & ExitSpeed & !hitter$HitType == "Bunt")
la <- hitter %>%
  filter(PitchCall == "InPlay" & Angle & !hitter$HitType == "Bunt")
so <- sum(str_count(hitter$KorBB, "Strikeout"))
pa <- inpl + walk + so
ab <- pa - walk - sac
avg <- hit / ab
obp <- (hit + walk) / pa
tb <- sum(s + (2 * do) + (3 * t) + (4 * hr)) 
slg <- tb / ab
ops <- obp + slg
```

Advanced Stats| | 
-|-|
AVG Exit Velocity: | `r sprintf("%.2f", mean(es$ExitSpeed, na.rm = TRUE))` mph
Max Exit Velocity: | `r sprintf("%.2f", max(es$ExitSpeed, na.rm = TRUE))` mph
AVG Launch Angle: | `r sprintf("%.2f", mean(la$Angle, na.rm = TRUE))` degrees
Max Estimated Distance: | `r sprintf("%.2f", max(hitter$Distance, na.rm = TRUE))` feet
Hard Hit Average | `r sprintf("%.3f", hhavg)`
Quality Contact Average | `r sprintf("%.3f", qhavg)`

```{r Split Stats}
pitcher_r <- hitter %>%
  filter(PitcherThrows == "Right")
s_r <- sum(str_count(pitcher_r$PlayResult, "Single"))
do_r <- sum(str_count(pitcher_r$PlayResult, "Double"))
t_r <- sum(str_count(pitcher_r$PlayResult, "Triple"))
hr_r <- sum(str_count(pitcher_r$PlayResult, "HomeRun"))
hit_r <- sum(s_r + do_r + t_r + hr_r)
inpl_r <- sum(str_count(pitcher_r$PitchCall, "InPlay"))
rbi_r <- sum(pitcher_r$RunsScored)
bb_r <- sum(str_count(pitcher_r$KorBB, "Walk"))
hbp_r <- sum(str_count(pitcher_r$PitchCall, "HitByPitch"))
walk_r <- sum(hbp_r + bb_r)
sac_r <- sum(str_count(pitcher_r, "Sacrifice"))
es_r <- pitcher_r %>%
  filter(PitchCall == "InPlay" & ExitSpeed & !pitcher_r$HitType == "Bunt")
la_r <- pitcher_r %>%
  filter(PitchCall == "InPlay" & Angle & !pitcher_r$HitType == "Bunt")
so_r <- sum(str_count(pitcher_r$KorBB, "Strikeout"))
pa_r <- inpl_r + walk_r + so_r
ab_r <- pa_r - walk_r - sac_r
avg_r <- hit_r / ab_r
obp_r <- (hit_r + walk_r) / pa_r
tb_r <- sum(s_r + (2 * do_r) + (3 * t_r) + (4 * hr_r)) 
slg_r <- tb_r / ab_r
ops_r <- obp_r + slg_r

pitcher_l <- hitter %>%
  filter(PitcherThrows == "Left")
s_l <- sum(str_count(pitcher_l$PlayResult, "Single"))
do_l <- sum(str_count(pitcher_l$PlayResult, "Double"))
t_l <- sum(str_count(pitcher_l$PlayResult, "Triple"))
hr_l <- sum(str_count(pitcher_l$PlayResult, "HomeRun"))
hit_l <- sum(s_l + do_l + t_l + hr_l)
inpl_l <- sum(str_count(pitcher_l$PitchCall, "InPlay"))
rbi_l <- sum(pitcher_l$RunsScored)
bb_l <- sum(str_count(pitcher_l$KorBB, "Walk"))
hbp_l <- sum(str_count(pitcher_l$PitchCall, "HitByPitch"))
walk_l <- sum(hbp_l + bb_l)
sac_l <- sum(str_count(pitcher_l, "Sacrifice"))
es_l <- pitcher_l %>%
  filter(PitchCall == "InPlay" & ExitSpeed & !pitcher_l$HitType == "Bunt")
la_l <- pitcher_l %>%
  filter(PitchCall == "InPlay" & Angle & !pitcher_l$HitType == "Bunt")
so_l <- sum(str_count(pitcher_l$KorBB, "Strikeout"))
pa_l <- inpl_l + walk_l + so_l
ab_l <- pa_l - walk_l - sac_l
avg_l <- hit_l / ab_l
obp_l <- (hit_l + walk_l) / pa_l
tb_l <- sum(s_l + (2 * do_l) + (3 * t_l) + (4 * hr_l)) 
slg_l <- tb_l / ab_l
ops_l <- obp_l + slg_l
```

Split Stats||
-|-|-
||*RHP*|*LHP*
AVG Exit Velocity:|`r sprintf("%.2f", mean(es_r$ExitSpeed, na.rm = TRUE))` mph|`r sprintf("%.2f", mean(es_l$ExitSpeed, na.rm = TRUE))` mph
AVG Launch Angle:|`r sprintf("%.2f", mean(la_r$Angle, na.rm = TRUE))` degrees|`r sprintf("%.2f", mean(la_l$Angle, na.rm = TRUE))` degrees