---
title: "Georgia Southern Pitching"
---

<hr>

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(ggplot2)
library(plotly)
library(data.table)
library(tidyr)
ncaa <- list.files("./NCAA", pattern = "*.csv", full.names = TRUE)
ncaa <- rbindlist(lapply(ncaa, fread))
geo_eag <- ncaa %>%
  filter(PitcherTeam == "GEO_EAG")
```

```{r Fastball/Player Filter}
fb <- geo_eag %>%
  filter(TaggedPitchType == "Fastball")
collins <- fb %>%
  filter(Pitcher == "Collins, Daniel")
edwards <- fb %>%
  filter(Pitcher == "Edwards, Jonathan")
harris <- fb %>%
  filter(Pitcher == "Harris, Hayden")
hays <- fb %>%
  filter(Pitcher == "Hays, Braden")
humphries <- fb %>%
  filter(Pitcher == "Humphries, Lawson")
johns <- fb %>%
  filter(Pitcher == "Johns, Braxton")
johnson <- fb %>%
  filter(Pitcher == "Johnson, David")
jones <- fb %>%
  filter(Pitcher == "Jones, Nick")
mcalister <- fb %>%
  filter(Pitcher == "McAlister, Aidan")
nahas <- fb %>%
  filter(Pitcher == "Nahas, Joe")
owens <- fb %>%
  filter(PitcherId == 1000054107)
parker <- fb %>%
  filter(Pitcher == "Parker, Jacob")
roberts <- fb %>%
  filter(Pitcher == "Roberts, Tristan")
shuman <- fb %>%
  filter(Pitcher == "Shuman, Seth")
whitney <- fb %>%
  filter(Pitcher == "Whitney, Cole")
```

|| **VELOCITY RANGE** | **SPIN RATE**
- |       -      |      - 
**DANIEL COLLINS** | `r sprintf("%.0f", range(collins$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(collins$SpinRate, na.rm = TRUE))`
**JONATHAN EDWARDS** | `r sprintf("%.0f", range(edwards$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(edwards$SpinRate, na.rm = TRUE))`
**HAYDEN HARRIS** | `r sprintf("%.0f", range(harris$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(harris$SpinRate, na.rm = TRUE))`
**BRADEN HAYS** | `r sprintf("%.0f", range(hays$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(hays$SpinRate, na.rm = TRUE))`
**LAWSON HUMPHRIES** | `r sprintf("%.0f", range(humphries$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(humphries$SpinRate, na.rm = TRUE))`
**BRAXTON JOHNS** | `r sprintf("%.0f", range(johns$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(johns$SpinRate, na.rm = TRUE))`
**DAVID JOHNSON** | `r sprintf("%.0f", range(johnson$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(johnson$SpinRate, na.rm = TRUE))`
**NICK JONES** | `r sprintf("%.0f", range(jones$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(jones$SpinRate, na.rm = TRUE))`
**AIDAN MCALISTER** | `r sprintf("%.0f", range(mcalister$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(mcalister$SpinRate, na.rm = TRUE))`
**JOE NAHAS** | `r sprintf("%.0f", range(nahas$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(nahas$SpinRate, na.rm = TRUE))`
**TYLER OWENS** | `r sprintf("%.0f", range(owens$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(owens$SpinRate, na.rm = TRUE))`
**JACOB PARKER** | `r sprintf("%.0f", range(parker$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(parker$SpinRate, na.rm = TRUE))`
**TRISTAN ROBERTS** | `r sprintf("%.0f", range(roberts$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(roberts$SpinRate, na.rm = TRUE))`
**SETH SHUMAN** | `r sprintf("%.0f", range(shuman$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(shuman$SpinRate, na.rm = TRUE))`
**COLE WHITNEY** | `r sprintf("%.0f", range(whitney$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(whitney$SpinRate, na.rm = TRUE))`

<hr>