---
title: "Chase Mascolo"
---

<hr>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, comment = NA, message = FALSE)
library(tidyverse)
library(ggplot2)
library(plotly)
library(data.table)
wake1 <- list.files("~/Appalachian State Baseball/Git Repositories/appstatebaseball/wake_files", pattern = "*.csv", full.names = TRUE)
wake <- rbindlist(lapply(wake1,fread))
Hitter <- wake %>%
  filter(Batter == "Mascolo, Chase")
```

```{r}
s <- sum(str_count(Hitter$PlayResult, "Single"))
do <- sum(str_count(Hitter$PlayResult, "Double"))
t <- sum(str_count(Hitter$PlayResult, "Triple"))
hr <- sum(str_count(Hitter$PlayResult, "HomeRun"))
hit <- sum(s + do + t + hr)
inpl <- sum(str_count(Hitter$PitchCall, "InPlay"))
rbi <- sum(Hitter$RunsScored)
bb <- sum(str_count(Hitter$KorBB, "Walk"))
hbp <- sum(str_count(Hitter$PitchCall, "HitByPitch"))
walk <- sum(hbp + bb)
sac <- sum(str_count(Hitter, "Sacrifice"))
es <- Hitter %>%
  filter(PitchCall == "InPlay" & ExitSpeed & !Hitter$HitType == "Bunt")
la <- Hitter %>%
  filter(PitchCall == "InPlay" & Angle & !Hitter$HitType == "Bunt")
so <- sum(str_count(Hitter$KorBB, "Strikeout"))
pa <- inpl + walk + so
ab <- pa - walk - sac
avg <- hit / ab
obp <- (hit + walk) / pa
tb <- sum(s + (2 * do) + (3 * t) + (4 * hr)) 
slg <- tb / ab
ops <- obp + slg
az <- data.frame(Hitter$BatterSide)
az <- az[1,1]
```

Batter Side: `r az` | | | | | | | Hitting Summary 
-|-|-|-|-|-|-|-
PA:|`r pa`| 2B:| `r do` | RBI: |`r rbi`| AVG: |`r round(avg, digits = 3)` |
AB: |`r ab` | 3B: | `r t` | BB: |`r bb` |SLG: | `r round(slg, digits = 3)`|
Hits: |`r hit`| HR: | `r hr` | HBP: | `r hbp` | OPS: | `r round(ops, digits = 3)`|
 | SO: |`r so` ||||| OBP: | `r round(obp, digits = 3)`

Hits| | 
-|-|
AVG Exit Velocity: | `r round(mean(es$ExitSpeed, na.rm = TRUE), digits = 2)` mph
Max Exit Velocity: | `r round(max(es$ExitSpeed, na.rm = TRUE), digits = 2)` mph
AVG Launch Angle: | `r round(mean(la$Angle, na.rm = TRUE), digits = 2)` degrees
Max Estimated Distance: | `r round(max(Hitter$Distance, na.rm = TRUE), digits = 2)` feet

<hr>