---
title: "Radford Pitching"
---

<hr>

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(ggplot2)
library(plotly)
library(data.table)
library(tidyr)
ncaa <- list.files("./NCAA", pattern = "*.csv", full.names = TRUE)
ncaa <- rbindlist(lapply(ncaa, fread))
rad_hig <- ncaa %>%
  filter(PitcherTeam == "RAD_HIG")
```

```{r Fastball/Player Filter}
fb <- rad_hig %>%
  filter(AutoPitchType == "Fastball")
boone <- fb %>%
  filter(Pitcher == "Boone, Cody")
bywaters <- fb %>%
  filter(Pitcher == "Bywaters, Ryan")
domecq <- fb %>%
  filter(Pitcher == "Domecq, Derek")
donovan <- fb %>%
  filter(Pitcher == "Donovan, Brandon")
dunn <- fb %>%
  filter(Pitcher == "Dunn, Cole")
feathers <- fb %>%
  filter(Pitcher == "Feathers, Brandon")
firoved <- fb %>%
  filter(Pitcher == "Firoved, Graham")
fritz <- fb %>%
  filter(Pitcher == "Fritz, Cameron")
gerber <- fb %>%
  filter(Pitcher == "Gerber, Austin")
hudson <- fb %>%
  filter(Pitcher == "Hudson, Bruce")
nardi <- fb %>%
  filter(Pitcher == "Nardi, Andrew")
reid <- fb %>%
  filter(Pitcher == "Reid, Colin")
ridgely <- fb %>%
  filter(Pitcher == "Ridgely, Zack")
threehouse <- fb %>%
  filter(Pitcher == "Threehouse, Evan")
williams <- fb %>%
  filter(Pitcher == "Williams, Hunter")
```

|| **VELOCITY RANGE** | **SPIN RATE**
- |       -      |      - 
**CODY BOONE** | `r sprintf("%.0f", range(boone$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(boone$SpinRate, na.rm = TRUE))`
**RYAN BYWATERS** | `r sprintf("%.0f", range(bywaters$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(bywaters$SpinRate, na.rm = TRUE))`
**DEREK DOMECQ** | `r sprintf("%.0f", range(domecq$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(domecq$SpinRate, na.rm = TRUE))`
**BRANDON DONOVAN** | `r sprintf("%.0f", range(donovan$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(donovan$SpinRate, na.rm = TRUE))`
**COLE DUNN** | `r sprintf("%.0f", range(dunn$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(dunn$SpinRate, na.rm = TRUE))`
**BRANDON FEATHERS** | `r sprintf("%.0f", range(feathers$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(feathers$SpinRate, na.rm = TRUE))`
**GRAHAM FIROVED** | `r sprintf("%.0f", range(firoved$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(firoved$SpinRate, na.rm = TRUE))`
**CAMERON FRITZ** | `r sprintf("%.0f", range(fritz$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(fritz$SpinRate, na.rm = TRUE))`
**AUSTIN GERBER** | `r sprintf("%.0f", range(gerber$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(gerber$SpinRate, na.rm = TRUE))`
**BRUCE HUDSON** | `r sprintf("%.0f", range(hudson$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(hudson$SpinRate, na.rm = TRUE))`
**ANDREW NARDI** | `r sprintf("%.0f", range(nardi$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(nardi$SpinRate, na.rm = TRUE))`
**COLIN REID** | `r sprintf("%.0f", range(reid$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(reid$SpinRate, na.rm = TRUE))`
**ZACK RIDGELY** | `r sprintf("%.0f", range(ridgely$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(ridgely$SpinRate, na.rm = TRUE))`
**EVAN THREEHOUSE** | `r sprintf("%.0f", range(threehouse$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(threehouse$SpinRate, na.rm = TRUE))`
**HUNTER WILLIAMS** | `r sprintf("%.0f", range(williams$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(williams$SpinRate, na.rm = TRUE))`

<hr>