---
title: "Louisiana Monroe Pitching"
---

<hr>

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)
library(tidyverse)
library(ggplot2)
library(plotly)
library(data.table)
library(tidyr)
ncaa <- list.files("./NCAA", pattern = "*.csv", full.names = TRUE)
ncaa <- rbindlist(lapply(ncaa, fread))
ulm_war <- ncaa %>%
  filter(PitcherTeam == "ULM_WAR")
```

```{r Fastball/Player Filter}
fb <- ulm_war %>%
  filter(TaggedPitchType == "Fastball")
bartonja <- fb %>%
  filter(Pitcher == "Barton, Jacob")
bartonju <- fb %>%
  filter(Pitcher == "Barton, Justin")
dunn <- fb %>%
  filter(Pitcher == "Dunn, Miles")
gray <- fb %>%
  filter(Pitcher == "Gray, Cole")
marsh <- fb %>%
  filter(Pitcher == "Marsh, Dylan")
```

|| **VELOCITY RANGE** | **SPIN RATE**
- |       -      |      - 
**JACOB BARTON** | `r sprintf("%.0f", range(bartonja$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(bartonja$SpinRate, na.rm = TRUE))`
**JUSTIN BARTON** | `r sprintf("%.0f", range(bartonju$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(bartonju$SpinRate, na.rm = TRUE))`
**MILES DUNN** | `r sprintf("%.0f", range(dunn$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(dunn$SpinRate, na.rm = TRUE))`
**COLE GRAY** | `r sprintf("%.0f", range(gray$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(gray$SpinRate, na.rm = TRUE))`
**DYLAN MARSH** | `r sprintf("%.0f", range(marsh$RelSpeed, na.rm = TRUE))` | `r sprintf("%.0f", mean(marsh$SpinRate, na.rm = TRUE))`

<hr>